Detecting Facial Expressions in Professional Tennis Matches

### 2017-08-11 Report06-12.Rmd
remove footnotes

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.)

@@

##Manual Annotation
To record the details of attributes for each face and scene a Shiny [@shiny] App was created. We called this Application our ManualClassificationProgram^[https://github.com/mvparrot/face-recognition/master/ManualClassificationProgram.R]. This helped to provide information for all attributes quickly and consistently.

@@

The collation of the results from the Manual Recognition Program created
two CSVs, ManualClassifiedFaces^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedFaces.csv] and ManualClassifiedScenes^[https://github.com/mvparrot/face-recognition/blob/master/ManualClassifiedScenes.csv].

@@

@@

## Player Faces

Tennis players faces will be the main focus of this use of facial detection. 
It is important that the selected API be able to return strong and consistent results for player's faces.

```{r Player, fig.cap = "This stacked bar chart allows consideration of the interaction between two image attributes. \\label{fig:DDPbgshot}"}

#ALLmetaIMGPlayers

ggplot(data=ALLmetaIMGPlayers) +
     geom_bar(aes(x=bg, fill = shotangle), 
            position = position_stack(reverse = TRUE), 
            na.rm=TRUE) +
  coord_flip() +
  guides(fill = guide_legend(title="Background")) +
  labs(caption="") +
  ylab("Amount of faces") + xlab("Angle the face was captured from")
```

@@

>>>>

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE)

@@

##Manual Annotation
To record the details of attributes for each face and scene a Shiny [@shiny] App was created. We called this Application our ManualClassificationProgram. This helped to provide information for all attributes quickly and consistently.

@@

The collation of the results from the Manual Recognition Program created
two CSVs.

@@

```{r GoogleRegression, fig.width=7.5, fig.cap = "Google Regression\\label{fig:GoogleRegression}"}
ALLmetaIMGnamedFaces %>% filter(type=="Manual" | type=="Google") %>%
  mutate(isplayer = ifelse(detect=="Player", 1, 0)) -> players

glm(isplayer ~ shotangle + bg + bg*shotangle + graphic + situation + lighting + glasses + visorhat, data=players) %>% summary()

# currently same model as earlier, give two?
```

@@

@@

All data files used are available on the github page.

ManualClassifiedFaces.csv resulted from the use of the Manual Classification Program, it has information about each face identified manually.
ManualClassifiedScenes.csv also resulted from the use of the app, it contains information about each image.
